---
title: "Proctor and Gamble Stock Volatility"
author: "Olivia Leeson"
date: "November 13, 2016"
output: 
  html_document:
    keep md: TRUE
---

## What are we doing?
This document shows how to download financial data using the tseries library and how to calculate stock returns and volatility. 

###Let's get Started
First we download our data for the stock of Proctor and Gamble from Yahoo! Finance. 
```{r}
#download tseries using download.packages("tseries") if not already installed
#call tseries library
library(tseries)
#uplaod data on PG stock at close
pgdata <- get.hist.quote('pg', quote="Close")
```

Now that we have our data downloaded, we want to calculate the returns and check how many historical observations we have available. 
```{r}
#calculate the day over day historical returns
pgreturn <- log(lag(pgdata)) - log(pgdata)
length(pgreturn)

```
It looks like we have 6518 returns to analyze. 
  

Next let's calculate the stocks' average volatility
```{r}
#find volatility. standard deviation of pgreturn times square root of 250
#250 is number of trading days/year
pgvol <- sd(pgreturn)*sqrt(250)*100
pgvol
```
The average volatility of Proctor and Gamble's stock is 32.75

##Now it's Time to Graph 

We are graphing estimated volatility for our Proctor and Gamble stock given varying values weights given to past volatilites. 

First we create our function that calculates volatility: 
```{r}
vol <- function(d, logrets){
  var=0
  lam=0
  varlist<- c()
  for (r in logrets){
    lam=lam*(1-1/d) +1
  var = (1 - 1/lam)*var + (1/lam)*r^2
    varlist <-c(varlist,var)
  }
  sqrt(varlist)
}
```


```{r}
#estimate volatility for varying ds, or weights
#gives high weight to past volatility
volest <-vol(10,pgreturn)
#gives medium weight to past volatility
volest2 <-vol(30,pgreturn)
#gives low weight to past volatility
volest3 <-vol(100,pgreturn)
```

From our graph we see that the lower the weight valued on past volatility, the smoother the volatility graph is with lower peaks.
```{r}
#plot volatilities 
plot(volest,type="l", col = "pink4")
lines(volest2, type="l", col="lightgreen")
lines(volest3, type="l", col="lightblue")
```